---
title: "*In vitro* expression - Nipah Virus Vaccine Concept"
output:
  html_document:
    theme: flatly       
    highlight: tango
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    self_contained: true
    css: "custom.css"
---




<br>

# Case Overview

---

**Nipah Virus Vaccine Concept**

Nipah virus infection is a zoonotic disease caused by an RNA(-) virus of the genus Henipavirus, associated with acute encephalitis, respiratory involvement, and high mortality in humans. Vaccine research targets the viral G glycoprotein to induce immune responses that block receptor binding and disease progression. In *mRNA* design, alpha-globin (*HBA1/HBA2*) UTRs are used to enhance stability and sustain protein expression in human cells.



---

<br>

# Project Overview


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("1.bmp")

```



---

<br>

# Design Workflow


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("2.bmp")

```





# Antigene Selection


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("3.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("4.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("5.bmp")

```




---

<br>


# Linker Selection


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("6.bmp")

```


---

<br>


# 5'UTR Selection



```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("7.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("8.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("9.bmp")

```


---

<br>


# 3'UTR Selection



```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("10.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("11.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("12.bmp")

```



---

<br>


# Polyadenylation Length



```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("13.bmp")

```



---

<br>


# Restriction Places for Remove



```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("14.bmp")

```


---

<br>


# Selection Marker

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("15.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("16.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("17.bmp")

```

---

<br>


# Calculations

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("18.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("19.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("20.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("21.bmp")

```


---

<br>


# Results


---


## Graphical Map of the Vector

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("22.bmp")

```

---

<br>


## FASTA Representation (Segmented)

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("23.bmp")

```

---

<br>


## FASTA Representation (Full Sequence)

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("24.bmp")

```


---

\

# Disclaimer

The designed therapeutic compounds presented here are solely the result of *in silico* analyses conducted using available databases, computational models, and template-based design approaches.

It should be emphasized that findings obtained through *in silico* methods are predictive in nature and therefore require further experimental validation. Critical confirmation of their actual efficacy, safety, and biological relevance must be achieved through *in vitro* studies, followed by *in vivo* investigations.

Only comprehensive experimental verification can enable a reliable assessment of the true therapeutic potential of the proposed compounds.

---

\
