---
title: "*In vitro* silencing - Familial Hypercholesterolemia disease"
output:
  html_document:
    theme: flatly       
    highlight: tango
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    self_contained: true
    css: "custom.css"
---




<br>

# Case Overview

---

**Familial Hypercholesterolemia**

An *in vitro* therapeutic approach for familial hypercholesterolemia may involve the use of T7 promoter-driven *shRNA* to selectively silence *PCSK9* expression in cultured hepatocytes. Reduced *PCSK9* levels can increase LDL receptor availability on the cell surface, enhancing cellular uptake of LDL particles. Measuring changes in *PCSK9* expression, receptor abundance, and LDL internalization enables preliminary evaluation of the strategy’s therapeutic potential.



---

<br>

# Project Overview


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("1.bmp")

```



---

<br>

# Design Workflow


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("2.bmp")

```



---

<br>


# Target Gene Selection for Silencing




```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("3.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("4.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("5.bmp")

```



---

<br>


# Loop Sequence Selection


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("6.bmp")

```


<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>



```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("7.bmp")

```


<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("7.2.bmp")

```

---

<br>


# Selection Marker



```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("8.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("9.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("10.bmp")

```



---

<br>

# Calculations

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("11.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("12.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("13.bmp")

```

<br>

<div style="text-align:center; font-size:48px; color:#9acd32; margin:20px 0;">
⬇
</div>

<br>


```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("14.bmp")

```

---

<br>


# Results


---


## Graphical Map of the Vector & shRNA

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("15.bmp")

```

---

<br>


## FASTA Representation (Segmented)

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("16.bmp")

```

---

<br>


## FASTA Representation (Full Sequence)

```{r echo=FALSE, out.width='90%', fig.align='center'}

knitr::include_graphics("17.bmp")

```


---

\

# Disclaimer

The designed therapeutic compounds presented here are solely the result of *in silico* analyses conducted using available databases, computational models, and template-based design approaches.

It should be emphasized that findings obtained through *in silico* methods are predictive in nature and therefore require further experimental validation. Critical confirmation of their actual efficacy, safety, and biological relevance must be achieved through *in vitro* studies, followed by *in vivo* investigations.

Only comprehensive experimental verification can enable a reliable assessment of the true therapeutic potential of the proposed compounds.

---

\
